\documentclass{beamer}
\usepackage{beamerthemeshadow}
\usepackage{graphicx}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[flushleft]{threeparttable}
\usepackage[english,serbian]{babel}
\definecolor{beamer@darkred}{rgb}{0.85,0.1,0.1}
\setbeamercolor{structure}{fg=beamer@darkred}


\title{Tehničko i naučno pisanje}
\subtitle{Kako i zašto funkcioniše blockchain?}
\author{Lazić Jovana, Nikić Ognjen, Nešković Ognjen, Sekešan Pavle}
\institute{Matematički fakultet\\Univerzitet u Beogradu}
\date{
	\footnotesize{Beograd, 2022.}	
}

\begin{document}
\begin{frame}
	\thispagestyle{empty}
	\titlepage
\end{frame}

\addtocounter{framenumber}{-1}

\begin{frame}[fragile]\frametitle{Literatura}
	\begin{itemize}
		\item G. Wood et al., “Ethereum: A secure decentralised generalised transaction ledger,” Ethereum project yellow paper, vol. 151, no. 2014, pp. 1-2, 2014.
		\item S. Nakamoto, “Bitcoin: A peer-to-peer electronic cash system,” Decentralized Business Review, p. 21260, 2008.
		\item H. S. Shin, “Chapter V Cryptocurrencies: looking beyond the hype,”BIS 2018 Annual Economic Report, 2018.
		\item V. Buterin, “A next-generation smart contract and decentralized application platform,” white paper, vol. 3, 2014.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Pregled} % Table of contents slide, comment this block out to remove it
	\tableofcontents[hidesubsections] 
\end{frame}

\section{Uvod}

\begin{frame}[fragile]\frametitle{Autentičnost dokumenata}
	
\end{frame}

\begin{frame}[fragile]\frametitle{Utvrđivanje hronologije}
	
\end{frame}

\begin{frame}[fragile]\frametitle{Verodostojan javni skup podataka - Blokčejn}
	
\end{frame}


\section{Kriptografske osnove}

\begin{frame}[fragile]\frametitle{Kriptografske heš funkcije - osobine}
	
\end{frame}

\begin{frame}[fragile]\frametitle{Kriptografske heš funkcije - algoritam}
	
\end{frame}

\begin{frame}[fragile]\frametitle{Asimetrična kriptografija}
	
\end{frame}


\section{Blokčejn}

\begin{frame}[fragile]\frametitle{Struktura blokčejna}
	
\end{frame}

\begin{frame}[fragile]\frametitle{Blokovi}
	
\end{frame}

\begin{frame}[fragile]\frametitle{Decentralizacija}
	
\end{frame}


\section{Primene}

\begin{frame}[fragile]\frametitle{Kriptovalute}
	
\end{frame}

\begin{frame}[fragile]\frametitle{Pametni ugovori}
	
\end{frame}

\begin{frame}[fragile]\frametitle{??}
	
\end{frame}


\section{Zaključak}

\begin{frame}[fragile]\frametitle{Zaključak}
	
\end{frame}

\end{document}